\documentclass{article}

\usepackage{tabularx}

\title{Outline}
\author{Matthew Robson}
\date{\today}


\begin{document}

\maketitle

\begin{abstract}
    This will be the place for my abstract where I can include the general idea behind the project and
    a sample of the conclusion and results.

\noindent
    At some point I will include my theory table. This theory table will include the following theories:

\end{abstract}

\section{Introduction}
Here I will define some terms and get the reader familiar with what the project will cover.  
\\
\\
\noindent
\begin{tabularx}{\textwidth}{|L|L|L|}
        \hline
        \textbf{Theory} & \textbf{Explaination} & \textbf{Reasoning} \\ \hline
        Subprime Loans lead to less secure housing & 
            Subprime loans ... &
            Subprime Loans lead to more single family housing lead to less multi-unit housing
              lead to higher housing costs and less housing in total \\ \hline

        Higher income leads to housing security &
            Something... &
            Place with higher income lead to housing developers building larger and better houses that 
              are then safer and more reddibly available so housing security is better \\ \hline

        Race has a correlation with housing security &
            something &
            There is a long standing understanding that intentional and unintentional seggregation has led 
              to seggregation in housing \\ \hline

\end{tabularx}

\subsection{Background}
This will specifically include what subprime loans are / what they are used for and the time period(s) that we 
are focusing on.

\subsection{Motivation}
Here I will specify why we are interested specifically in the long tail impacts of subprime loans. 

\subsection{Literature Gaps?}
Here I might include some information on how other papers have avoided this topic and how this paper will
be unique.

\subsection{Overview of Methodology}
Here I will include the general idea behind the structure of the paper and the way that we will attempt to
answer our given question.

%%=======================%% Literature Review %%=======================%%
\section{Literature Review}
Here I will cover information provided by many other articles that cover the information that may be found
in this paper. Along with this, I will contextualize the problem in the space of other tried methodologies 
and papers. (there will probably be some subsections but idk what they will be called)

%%=======================$% Methods %%=======================%%
\section{Methods}
I will covere the methods that we took to get this data an anlyze it.

\subsection{Data Collection and Choice}
Here I will cover why I choose the data that I did.

\subsection{Variable Analysis}
I will talk about why certain variable are important and how they will be derived from the data that we 
aquired. 

\subsection{Modeling}
This will contain information on how the models were generated and why they were made in this way.

%%=======================%% Results %%=======================%%
\section{Results}
I will discuss what our results are including relevent figures and context. (again probably there will be 
some subsections but idk what they will be yet)

%%=======================%% Discussion %%=======================%%
\section{Discussion}
Now I will finally start expanding back up to larger generalizations and how the results may impact the 
wider housing market and even other financial markets. (probably subsections for each large impact)

%%=======================%% References %%=======================%%
\section{References}
bibtex probably...

\end{document}
